---
title: "Web Exercise 9"
author: Merlin Schaeffer & Friedolin Merhout
output: webexercises::webexercises_default
date: 2022-10-21
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE, servr.interval = 0.5, width = 115, digits = 2)
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, fig.retina = 3, error = TRUE,
  warning = FALSE, cache = FALSE, fig.align='center',
  comment = "#", strip.white = TRUE)

# Add packages to library
library(tidyverse) # Add the tidyverse package to my current library.
library(haven) # Handle labelled data.
library(ggplot2) # Allows us to create nice figures.
library(estimatr) # Allows us to estimate (cluster-)robust standard errors
library(texreg) # Allows us to make nicely-formatted Html & Latex regression tables.
library(broom) # Allows us to turn parts of model objects into tibbles.
library(modelr) # Model predictions (can also do resampling).
library(webexercises)


# Load the previously downloaded ESS round 10 data
ESS <- read_spss("./../../assets/ESS10.sav")

ESS <- ESS %>% transmute( # Create new variables and keep only those
  cntry = as_factor(cntry), # Country of interview
  gndr = as_factor(gndr),
  facntr = as_factor(facntr), # Father born in cntry
  mocntr = as_factor(mocntr), # Mother born in cntry
  imwbcnt = max(imwbcnt, na.rm = TRUE) - zap_labels(imwbcnt),
  # Religion
  rlgblg = as_factor(rlgblg), # Belonging to a religion
  rlgdgr = case_when( # How religious
    rlgblg == "No" ~ 0,
    TRUE ~       zap_labels(rlgdgr)),
  rlgatnd = case_when( # Service attendance
    rlgblg == "No" ~ 0,
    TRUE ~ max(rlgatnd, na.rm = TRUE) - zap_labels(rlgatnd)),
  pray = case_when( # Prayer frequency
    rlgblg == "No" ~ 0,
    TRUE ~ max(pray, na.rm = TRUE) - zap_labels(pray)),
    pspwght = pweight*dweight,
  # Parental education (ISCED) #<<
  eiscedf = zap_labels(eiscedf), #<<
  eiscedm = zap_labels(eiscedm), #<<
  par_edu = case_when( #<<
    # If father's edu is missing but not mother's, take mother's #<<
    (eiscedf == 55 | is.na(eiscedf)) & eiscedm != 55 & !is.na(eiscedm) ~ eiscedm, #<<
    # If mother's edu is missing but not father's, take father's #<<
    (eiscedm == 55 | is.na(eiscedm)) & eiscedf != 55 & !is.na(eiscedf)  ~ eiscedf, #<<
    # If both are missing, its missing #<<
    eiscedf == 55 & eiscedm == 55 ~ as.numeric(NA), #<<
    # For all others, take the average of both parents #<<
    TRUE ~ (eiscedm + eiscedf) / 2), #<<
  eduyrs = case_when( # Education
    eduyrs > 21 ~ 21, # Recode to max 21 years of edu.
    eduyrs < 9 ~ 9, # Recode to min 9 years of edu.
    TRUE ~ zap_labels(eduyrs))) %>% # Make it numeric, then
  dplyr::filter( # Keep only respondents with native-born parents in four countries
    facntr == "Yes" & mocntr == "Yes",
    cntry %in% c("France", "Estonia", "Finland", "Hungary"))
```

1) Use the set-up of exercise 7. Drop unused factor levels in `cntry`, and make a design matrix like I did in my slides (i.e., keep only `imwbcnt`, `rlgblg`, `rlgdgr`, `rlgatnd`, `pray`, `cntry`, `par_edu`, `gndr`, `pspwght`, and apply casewise deletion). That design matrix has `r fitb("5817", width = "4")` observations left.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
ESS <- ESS %>%
  mutate(
    cntry = fct_drop(cntry)
  ) %>%
  select(imwbcnt, rlgdgr, rlgatnd, eduyrs, par_edu, cntry, gndr, pspwght) %>%
  drop_na()
```
`r unhide()`

2) Regress xenophobia on the importance of religion and frequency of religious service attendance; does the importance of religion have a curve-shaped relationship with xenophobia? Make sure to not use orthogonal polynomials for this question. `r mcq(c("No", "Yes, religiosity goes along with declining levels of xenophobia, but that relationship vanishes", "Yes, religiosity goes along with declining levels of xenophobia, and that relationship grows exponentially", answer = "Yes, initially religiosity goes along with increased xenophobia, but then that relationship declines in strength"))`
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
ols1 <- lm_robust(imwbcnt ~ poly(rlgdgr, 2, raw = TRUE) + rlgatnd, w = pspwght, data = ESS)
screenreg(ols1, include.ci = FALSE)
```
`r unhide()`

3) Model 3: Add `eduyrs`, `par_edu`, `cntry`, and `gndr` as control variables, what happens to our curvi-linear religiosity estimates? `r mcq(c(answer = "The main term declines in strength, but not at all the squared term", "They all turn insignificant", "Particularly the main, but also the squared term decline in strength but significance does not change", "Only the squared term declines in strength"))`
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
ols2 <- lm_robust(imwbcnt ~ poly(rlgdgr, 2, raw = TRUE) + rlgatnd + eduyrs + par_edu + cntry + gndr, w = pspwght, data = ESS)
screenreg(ols2, include.ci = FALSE)
```
`r unhide()`

4) Visualize the relationship (i.e., visualize the predictions from your model.).
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
# Generate synthetic data to 
# visualize religious importance
synth_data <- ESS %>%
   # Generate theoretically-informative 
   # but artificial tibble for predictions.
   data_grid(par_edu, gndr, cntry, rlgdgr, rlgatnd) %>%
   mutate( # Set confounders constant at their mean or mode respectively,
     eduyrs = mean(ESS$eduyrs, na.rm = TRUE),
     par_edu = mean(ESS$par_edu, na.rm = TRUE),
     rlgatnd = mean(ESS$rlgatnd, na.rm = TRUE),
     gndr = "Female",
     cntry = "Hungary") %>% # then
   unique() # Drop duplicates.

# Generate predictions and 95% confidence intervals, then
synth_data <- predict(ols2, newdata = synth_data,
                      interval = "confidence",
                      level = 0.95)$fit %>%
  as_tibble() %>% # Turn into a tibble, then
  bind_cols(synth_data, .) # Add to the synthetic data.


ggplot(data = synth_data, aes(y = fit, x = rlgdgr)) +
  geom_ribbon(aes(ymin = lwr, ymax = upr), alpha = 0.5) +
  geom_line() +
  labs(x = "Importance of religion",
  y = "Xenophobia",
  caption = "(Covariates set to: French women\n at mean levels of religious attendance,\n and own and parental education.") + 
  theme_minimal()
```
`r unhide()`

5) Is the relation between parental education and xenophobia conditional on the country of residence? Z-standardize parental education using `I()`. `r mcq(c("No, it is not statistically different across the countries", answer = "Yes, in Finland and Hungary parental education is a less important predictor of xenophobia than in Estonia", "Yes, in France parental education is a more important predictor of xenophobia than in Estonia", "Yes, in Hungary parental education is a less important predictor of xenophobia than in Finland"))`
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
ols3 <- lm_robust(imwbcnt ~ poly(rlgdgr, 2, raw = TRUE) + rlgatnd + eduyrs + I(scale(par_edu))*cntry + gndr, w = pspwght, data = ESS)
screenreg(ols3, include.ci = FALSE)
```
`r unhide()`

6) Visualize the interaction effect.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
# Generate synthetic data to 
# visualize parental education
synth_data <- ESS %>%
   # Generate theoretically-informative 
   # but artificial tibble for predictions.
   data_grid(par_edu, gndr, cntry, rlgdgr, rlgatnd) %>%
   mutate( # Set confounders constant at their mean or mode,
     rlgdgr = mean(ESS$rlgdgr, na.rm = TRUE),
     rlgatnd = mean(ESS$rlgatnd, na.rm = TRUE),
     eduyrs = mean(ESS$eduyrs, na.rm = TRUE),
     gndr = "Female") %>% # then
   unique() # Drop duplicates.

# Generate predictions and 95% confidence intervals, then
synth_data <- predict(ols3, newdata = synth_data,
                      interval = "confidence",
                      level = 0.95)$fit %>%
  as_tibble() %>% # Turn into a tibble, then
  bind_cols(synth_data, .) # Add to the synthetic data.


ggplot(data = synth_data, aes(y = fit, x = par_edu)) +
  geom_ribbon(aes(ymin = lwr, ymax = upr, fill = cntry), alpha = 0.5) +
  geom_line(aes(color = cntry)) +
  labs(x = "Parental education",
       y = "Xenophobia",
       caption = "(Covariates set to: Women at mean levels of education, religiosity, and religious service attendance)",
       color = "Country", fill = "Country") + 
  theme_minimal() +
  theme(legend.position = c(0.87, 0.8),
        legend.background = 
          element_rect(fill = NA,
                       color = NA))
```
`r unhide()`
