---
title: "Web Exercise 3"
author: Merlin Schaeffer
output: webex::webex_default
date: 2021-02-15
publishdate: 2021-02-12
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE, servr.interval = 0.5, width = 115, digits = 2)
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, 
  warning = FALSE, cache = FALSE,
  comment = "#", strip.white = TRUE)

library(webex)
```


1. Import the ESS round 9 data using the API.
`r hide("R solution -> dont' peek to early ;) !")`
```{r eval = FALSE}
# Add packages to library
library(tidyverse) # Add the tidyverse package to my current library.
library(haven) # Handle labelled data.
library(essurvey) # Add ESS API package to library.

# Import the ESS round 9 data via the API
ESS <- import_rounds(rounds = 9, ess_email = "YOUR-EMAIL", format = "spss")
```

```{r include = FALSE}
# Add packages to library
library(tidyverse) # Add the tidyverse package to my current library.
library(haven) # Handle labelled data.
library(essurvey) # Add ESS API package to library.

# Import the ESS round 9 data via the API
ESS <- import_rounds(rounds = 9, ess_email = "merlin.schaeffer@uni-koeln.de", format = "spss")
```
`r unhide()`

2. Keep only a person and a country identifier, the post-stratification weights, `eduyrs`, `agea`, `dscrgrp`, and the homophobia variables that you identified. The function that allows you to do that is called `r fitb("select()", width = "8")`.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
(ESS <- select(ESS, idno, cntry, pspwght,
               eduyrs, agea, dscrgrp, 
               freehms, hmsfmlsh, hmsacld))
```
`r unhide()`

3. Change the variables into numeric and factors appropriately. For that, you need the two functions `r fitb("zap_labels()", width = "12")` for numeric and `r fitb("as_factor()", width = "11")` for categorical variables.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
ESS <- mutate(ESS,
              idno = zap_labels(idno),
              cntry = as_factor(cntry),
              pspwght = zap_labels(pspwght),
              eduyrs = zap_labels(eduyrs),
              agea = zap_labels(agea),
              dscrgrp = as_factor(dscrgrp),
              freehms = zap_labels(freehms),
              hmsfmlsh = zap_labels(hmsfmlsh),
              hmsacld = zap_labels(hmsacld)
)
```
`r unhide()`

4. Z-standardize `eduyrs` and `agea`. Remember, $z_x = \frac{x - \bar{x}}{\text{SD(x)}}$.
`r hide("R solution -> dont' peek to early ;) !")`
```{r error = TRUE}
# First. check whether values on those variables make sense.
summary(ESS$eduyrs) # 0 or 55 years of education?
summary(ESS$agea) # Age seems fine.

# Second, recode.
ESS <- mutate(ESS,
              # Recode to max 21 years of edu.
              eduyrs = case_when(
                eduyrs > 21 ~ 21,
                eduyrs < 9 ~ 9,
                TRUE ~ as.numeric(eduyrs)
              ),
              # z-standardize
              z_eduyrs = (eduyrs - mean(eduyrs, na.rm = TRUE)) / sd(eduyrs, na.rm = TRUE),
              z_agea = (agea - mean(agea, na.rm = TRUE)) / sd(agea, na.rm = TRUE)
)

summary(ESS$z_eduyrs)
summary(ESS$z_agea)
```
`r unhide()`

5. Recode `dscrgrp` to "Yes" for all persons older than 80 in Germany, and to "No" for all respondents with more than average years of education in France. Use the `table()` function to show the frequency of `dscrgrp` by country. After the recode, `r fitb("166", width = "3")` respondents from Germany answered that they belong to a discriminated minority, and `r fitb("263", width = "3")` from France.
`r hide("R solution -> dont' peek to early ;) !")`
```{r error = TRUE}
ESS <- mutate(ESS,
              dscrgrp = case_when( # Start complex recode
                # Older than 80 & Germany ~ "Yes",
                agea > 80 & cntry == "DE" ~ "Yes", 
                # Older than mean & France
                eduyrs > mean(eduyrs, na.rm = TRUE) & cntry == "FR" ~ "No",
                # All others ~ as before, need to make it character for type consistency.
                TRUE ~ as.character(dscrgrp) 
              ),
              # Now make it a factor again.
              dscrgrp = factor(dscrgrp) 
)

# ... don't forget to check your recode for bugs!

# Absolute frequencies cross-table.
table(ESS$dscrgrp, ESS$cntry) # Israel, no surprise 20% are Arab in this contested state.
```
`r unhide()`

6. Now check out `prop.table()` and find out how to use it. In which country do most people report discrimination (apart from Germany and France, which we messed up ...)?

`r mcq(c("Belgium followed by Austria", "Serbia followed by Hungary", answer = "The UK followed by Serbia", "Czech Republic followed by Finland"))`

`r hide("R solution -> dont' peek to early ;) !")`
```{r}
# Relative frequencies cross-table.
prop.table(table(ESS$dscrgrp, ESS$cntry), margin = 1) # Relative frequencies. With 24.6% it is still Israel, followed by the UK.
```
`r unhide()`

7. Show the frequency table only for respondents who are older than 45.
`r hide("R solution -> dont' peek to early ;) !")`
```{r error = TRUE}
# Use the index to select cases
prop.table(table(ESS$cntry[ESS$agea > 45], ESS$dscrgrp))

# You need to make sure to select the same cases for both variables!
prop.table(table(ESS$cntry[ESS$agea > 45], ESS$dscrgrp[ESS$agea > 45]))
```
`r unhide()`

8. How did you filter the cases; would there have been another way?
`r hide("R solution -> dont' peek to early ;) !")`
```{r error = TRUE}
# Use filter() to generate a new tibble that contains only cases who are older than 45.
ESS_46Plus <- filter(ESS, agea > 45)

prop.table(table(ESS_46Plus$cntry, ESS_46Plus$dscrgrp))
```
`r unhide()`