---
title: "Web Exercise 1"
author: Merlin Schaeffer
output: webex::webex_default
date: 2021-02-08
publishdate: 2021-01-25
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE, servr.interval = 0.5, width = 115, digits = 2)
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, 
  warning = FALSE, cache = FALSE,
  comment = "#", strip.white = TRUE)

library(webex)
```

I suggest you create a new R Script "Exercises.R" that contains your solutions, so you don't intermix exercises with lecture notes.

1. Why does the code below throw an error? Explain, and then solve the problem.
```{r error = TRUE}
Oh_a_new_object <- 10
0h_a_new_object
```
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
Oh_a_new_object <- 10
Oh_a_new_object # Exchange the number 0 for the letter O #<<
```
`r unhide()`

2. Create an object `another_object2` that contains whole numbers from 123 to 131. The name of the function allowing you to do that is: `r fitb("seq()", width = "5")` and the assignment operator that creates the object is `r fitb("<-", width = "2")`.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
(another_object2 <- seq(123, 131))
```
`r unhide()`

3. Let R evaluate which of `another_object2`'s elements is larger than 128 and smaller than 130.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
another_object2 > 128 & another_object2 < 130
```
`r unhide()`

4. Add 2 to each element of another_object2 and check again which of its elements is larger than 128 and smaller than 130.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
another_object2 <- another_object2 + 2
another_object2 > 128 & another_object2 < 130
```
`r unhide()`

5. Create an object `another_textobject` that contains the sentence: "I am just another sentence."
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
(another_textobject <- "I am just another sentence.")
```
`r unhide()`

6. What does R return if you try to multiply `another_textobject` by 3?
```{r echo = FALSE}
another_textobject <- "I am just another sentence."
```
`r mcq(c(answer = "non-numeric argument to binary operator", "type mismatch", "'I am just another sentence.' 'I am just another sentence.' 'I am just another sentence.'"))`
`r hide("R solution -> dont' peek to early ;) !")`
```{r error = TRUE}
another_textobject <- another_textobject * 3
```
`r unhide()`

7. Use the `rep()` function to repeat `another_textobject` five times. The argument to which you need to supply the value 5 is called `r fitb("times", width = "5")`.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
rep(another_textobject, times = 5)
```
`r unhide()`

8. Use the `rep()` function to repeat `another_object2` three times.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
rep(another_object2, times = 5)
```
`r unhide()`

9. Use the `rep()` function to repeat *each element* of `another_object2` three times. The argument to which you need to supply the value 3 is called `r fitb("each", width = "4")`.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
rep(another_object2, each = 3)
```
`r unhide()`