---
title: "Web Exercise 3"
author: Merlin Schaeffer & Friedolin Merhout
output: webexercises::webexercises_default
date: 2022-10-19
publishdate: 2021-02-12
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE, servr.interval = 0.5, width = 115, digits = 2)
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, 
  warning = FALSE, cache = FALSE,
  comment = "#", strip.white = TRUE)

library(webexercises)
```

Some preparation:
```{r setup2, include = FALSE}
options(htmltools.dir.version = FALSE, servr.interval = 0.5, width = 115, digits = 2)
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, fig.align='center',
  warning = FALSE, cache = FALSE, fig.retina = 2,
  comment = "#", strip.white = TRUE)

# Add packages to library
library(tidyverse) # Add the tidyverse package to my current library.
library(haven) # Handle labelled data.
library(ggplot2) # Allows us to create nice figures.
library(webexercises) # Create interactive web pages that students can use in self-guided learning.
```

```{r include  = FALSE}
# Import the ESS round 10
ESS <- read_spss("./../../assets/ESS10.sav")
```

```{r}
ESS <- transmute(ESS, # Recode several variables & keep only the recoded ones (i.e., transmute vs mutate). #<<
                 idno = zap_labels(idno),
                 # Make the following variables factors:
                 cntry = as_factor(cntry) %>% fct_drop(), 
                 agea = zap_labels(agea),
                 pspwght = pweight*dweight)
```

```{r include = FALSE}
ESS_keep <- ESS
```

```{r}
ESS <- dplyr::filter(ESS,
                     # Only respondents from Eastern European countries:
                     (cntry %in% c("Slovakia", "Hungary", "Czechia", "Slovenia"))
)

# Casewise deletion of missing values
ESS <- drop_na(ESS)
```

1. Get the ggplot2 [cheat sheet](https://www.rstudio.com/resources/cheatsheets/), and check out the [reference page of ggplot2](https://ggplot2.tidyverse.org/reference/). Look at geoms for univariate (one variable) figures. Make an appropriate (weighted) figure that describes the distribution of `cntry`. Which country (Slovakia, Hungary, Czechia, or Slovenia) has the largest number of observations? `r mcq(c("Slovenia", answer = "Czechia", "Hungary", "Slovakia"))`
    + Throughout all figures, learn how to use `labs()` (i.e., learn it from the [reference page of ggplot2](https://ggplot2.tidyverse.org/reference/)).
`r hide("R solution -> dont' peek to early ;) !")`
```{r out.width='85%', fig.width = 6, fig.height = 3}
ggplot(data = ESS) +
  geom_bar(aes(x = cntry, weight = pspwght)) +
  labs(x = "Country of interview")
```
`r unhide()`

2. Make an appropriate (weighted) figure that describes the distribution of `agea`. Across all four countries, are there more or less than 20 respondents who are older than 100? `r mcq(c("More", answer = "Less"))`
`r hide("R solution -> dont' peek to early ;) !")`
```{r out.width='85%', fig.width = 6, fig.height = 3}
ggplot(data = ESS) +
  geom_histogram(aes(x = agea, weight = pspwght)) +
  labs(x = "Age")
```
`r unhide()`