---
title: "Web Exercise 10"
author: Merlin Schaeffer
output: webex::webex_default
date: 2020-03-04
publishdate: 2020-03-04
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE, servr.interval = 0.5, width = 115, digits = 2)
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, fig.retina = 3, error = TRUE,
  warning = FALSE, cache = FALSE, fig.align='center',
  comment = "#", strip.white = TRUE)

# Add packages to library
library(tidyverse) # Add the tidyverse package to my current library.
library(haven) # Handle labelled data.
library(essurvey) # Add ESS API package.
library(ggplot2) # Allows us to create nice figures.
library(factoextra) # Allows us to visualize PCAs
library(psych) # Supports PCA & factor analysis with several useful functions.
library(estimatr) # Allows us to estimate (cluster-)robust standard errors
library(texreg) # Allows us to make nicely-formatted Html & Latex regression tables.
library(broom) # Allows us to turn parts of model objects into tibbles.
library(modelr) # Model predictions (can also do resampling).
library(webex)

# Import the ESS round 9 data via the API
ESS <- import_rounds(rounds = 9, ess_email = "merlin.schaeffer@uni-koeln.de", format = "spss")

ESS <- ESS %>% transmute( # Create new variables and keep only those
    cntry = as_factor(cntry) %>% fct_relevel("Denmark"), # Country of interview
    gndr = as_factor(gndr), # Gender
    facntr = as_factor(facntr), # Father born in cntry
    mocntr = as_factor(mocntr), # Mother born in cntry
    imbgeco = max(imbgeco, na.rm = TRUE) - zap_labels(imbgeco),
    imueclt = max(imueclt, na.rm = TRUE) - zap_labels(imueclt),
    imwbcnt = max(imwbcnt, na.rm = TRUE) - zap_labels(imwbcnt),
    # Regigion
    rlgblg = as_factor(rlgblg), # Belonging to a religion
    rlgdgr = zap_labels(rlgdgr), # How religios
    rlgatnd = max(rlgatnd, na.rm = TRUE) - zap_labels(rlgatnd), # Service attendance
    pray = max(pray, na.rm = TRUE) - zap_labels(pray), # PRayer frequency
    pspwght = zap_labels(pspwght),
    # Parental education (ISCED) #<<
    eiscedf = zap_labels(eiscedf), #<<
    eiscedm = zap_labels(eiscedm), #<<
    par_edu = case_when( #<<
      # If father's edu is missing but not mother's, take mother's #<<
      (eiscedf == 55 | is.na(eiscedf)) & eiscedm != 55 & !is.na(eiscedm) ~ eiscedm, #<<
      # If mother's edu is missing but not father's, take father's #<<
      (eiscedm == 55 | is.na(eiscedm)) & eiscedf != 55 & !is.na(eiscedf)  ~ eiscedf, #<<
      # If both are missing, its missing #<<
      eiscedf == 55 & eiscedm == 55 ~ as.numeric(NA), #<<
      # For all others, take the average of both parents #<<
      TRUE ~ (eiscedm + eiscedf) / 2), #<<
    eduyrs = case_when( # Education
      eduyrs > 21 ~ 21, # Recode to max 21 years of edu.
      eduyrs < 9 ~ 9, # Recode to min 9 years of edu.
      TRUE ~ zap_labels(eduyrs))) %>% # Make it numeric, then
  dplyr::filter(
    # Keep only respondents with native-born parents,
    facntr == "Yes" & mocntr == "Yes" &
       (cntry == "Denmark" | cntry == "Sweden" | cntry == "Norway" | cntry == "Germany"))

# Conduct PCA of climate change concerns
(pca <- ESS %>% prcomp(
  formula = ~ imbgeco + imueclt + imwbcnt + 
    rlgdgr + rlgatnd + pray,
  data = ., na.action = na.exclude,
  center = TRUE, scale = TRUE))

# Show importance of single components.
summary(pca) 

# Oblique rotation
(oblique_solution <- promax(
  # of first two PCs
  pca$rotation[, c("PC1", "PC2")]))

# Visualize the results
pca$rotation <- oblique_solution$loadings
fviz_pca_var(pca, # Visualize PCA object
             # Color by contributions to the PC
             col.var = "contrib",
             # From blue to red.
             gradient.cols = c(low = "#00AFBB", 
                               mid = "#E7B800", 
                               high = "#FC4E07"))

# Generate new component scores for every respondent based on the 
# rotated principal components and write the into object "rotated_PCs"
rotated_PCs <- ESS %>% 
  dplyr::select(imbgeco, imueclt, imwbcnt, 
    rlgdgr, rlgatnd, pray) %>% 
  factor.scores(x = ., f = pca$rotation)
# Add a "xeno" and "relig" from "rotated_PCs" to our data.
ESS[, c("xeno", "relig")] <- rotated_PCs$scores
```

1) Use the set-up of exercise 9 (i.e., taks 1 and 2). Z-standardize `xeno`, drop unused factor levels in `cntry`, and make a design matrix like I did in my slides (i.e., keep only `xeno`, `relig`, `cntry`, `par_edu`, `gndr`, `pspwght`, and apply casewise deletion). That design matrix has `r fitb("5197", width = "4")` observations left.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
ESS <- ESS %>%
  mutate(
    xeno = scale(xeno) %>% as.numeric(),
    cntry = fct_drop(cntry)
  ) %>%
  select(xeno, relig, eduyrs, par_edu, cntry, gndr, pspwght) %>%
  drop_na()
```
`r unhide()`

2) Regress xenophobia on religiosity; does religiosity have a curve-shaped relationship with xenophobia? Make sure to not use orthogonal polynomials for this question. `r mcq(c("Yes, initially religiosity goes along with increased xenophobia, but then that relationship declines in strength", "Yes, religiosity goes along with declining levels of xenophobia, but that relationship vanishes", "Yes, religiosity goes along with declining levels of xenophobia, and that relationship grows exponentially", answer = "No"))`
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
ols1 <- lm_robust(xeno ~ poly(relig, 2, raw = TRUE), w = pspwght, data = ESS)
screenreg(ols1, include.ci = FALSE)
```
`r unhide()`

3) Model 3: Add `cntry`, `par_edu`, `agea', and `gndr` as control variables, what happens to our two religiosity estimates? `r mcq(c(answer = "They somewhat change but remain insignificant", "Particularly the main, but also the squared term decline in strength", "The main term declines in strength, but not at all the squared term", "Only the squared term declines in strength"))`
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
ols2 <- lm_robust(xeno ~ poly(relig, 2, raw = TRUE) + par_edu + cntry + gndr, w = pspwght, data = ESS)
screenreg(ols2, include.ci = FALSE)
```
`r unhide()`

4) Visualize the (not really curve-linear) relationship (i.e., visualize the predictions from your model.).
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
# Generate synthetic data to 
# visualize parental education
synth_data <- ESS %>%
   # Generate theoretically-informative 
   # but artificial tibble for predictions.
   data_grid(par_edu, gndr, cntry, relig) %>%
   mutate( # Set confounders constant at their mean,
     eduyrs = mean(ESS$eduyrs, na.rm = TRUE),
     par_edu = mean(ESS$par_edu, na.rm = TRUE),
     gndr = "Female",
     cntry = "Denmark") %>% # then
   unique() # Drop duplicates.

# Generate predictions and 95% confidence intervals, then
synth_data <- predict(ols2, newdata = synth_data,
                      interval = "confidence",
                      level=0.95)$fit %>%
  as_tibble() %>% # Turn into a tibble, then
  bind_cols(synth_data, .) # Add to the synthetic data.


ggplot(data = synth_data, 
       aes(y = fit, x = relig)) +
  geom_ribbon(aes(ymin = lwr, ymax = upr), 
              alpha = 0.5) +
  geom_line() +
  labs(x = "Religiosity",
  y = "Xenophobia",
  caption = "(Covariates set to: German women at mean levels of (parental) education)") + 
  theme_minimal()
```
`r unhide()`

5) Is the relation between parental education and xenophobia conditional on the country of residence? `r mcq(c("No, it is not statistically different across the countries", answer = "Yes, in Germany parental education is a more important predictor of xenophobia than in Denmark", "Yes, in Sweden and Norway parental education is a less important predictor of xenophobia than in Denmark", "Yes, in Norway parental education is a less important predictor of xenophobia than in Denmark"))`
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
ols3 <- lm_robust(xeno ~ poly(relig, 2, raw = TRUE) + par_edu*cntry + gndr, w = pspwght, data = ESS)
screenreg(ols3, include.ci = FALSE)
```
`r unhide()`

6) Visualize the interaction effect.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
# Generate synthetic data to 
# visualize parental education
synth_data <- ESS %>%
   # Generate theoretically-informative 
   # but artificial tibble for predictions.
   data_grid(par_edu, gndr, cntry, relig) %>%
   mutate( # Set confounders constant at their mean,
     relig = mean(ESS$relig, na.rm = TRUE),
     eduyrs = mean(ESS$eduyrs, na.rm = TRUE),
     gndr = "Female") %>% # then
   unique() # Drop duplicates.

# Generate predictions and 95% confidence intervals, then
synth_data <- predict(ols3, newdata = synth_data,
                      interval = "confidence",
                      level=0.95)$fit %>%
  as_tibble() %>% # Turn into a tibble, then
  bind_cols(synth_data, .) # Add to the synthetic data.


ggplot(data = synth_data, 
       aes(y = fit, x = par_edu)) +
  geom_ribbon(aes(ymin = lwr, ymax = upr, fill = cntry), alpha = 0.5) +
  geom_line(aes(color = cntry)) +
  labs(x = "Parental education",
  y = "Xenophobia",
  caption = "(Covariates set to: Women at mean levels of education and religiosity)") + 
  theme_minimal()
```
`r unhide()`
