---
title: "Web Exercise 2"
author: Merlin Schaeffer & Friedolin Merhout
output: webexercises::webexercises_default
date: 2022-10-19
publishdate: 2021-01-25
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE, servr.interval = 0.5, width = 115, digits = 2)
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, 
  warning = FALSE, cache = FALSE,
  comment = "#", strip.white = TRUE)

library(webexercises)
library(tidyverse)

options(htmltools.dir.version = FALSE, servr.interval = 0.5, width = 115, digits = 2)
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, 
  warning = FALSE, cache = FALSE,
  comment = "#", strip.white = TRUE)
```


1. Create a factor vector called `conti` with the five observations: "Europe", "Africa", "Africa", "Asia", "S.America" and the six levels: "Africa", "Asia", "Australia", "Europe", "N.America", "S.America". Make sure to print it right away.
`r hide("R solution -> dont' peak to early ;) !")`
```{r}
(conti <- factor(
  x = c("Europe", "Africa", "Africa", "Asia", "S.America"),
  levels = c("Africa", "Asia", "Australia",
             "Europe", "N.America", "S.America")
))
```
`r unhide()`

2. Recode the continent variable into your native language or another language you know. To do that, we use the `r fitb("fct_recode()", width = "10")` function from the forcats package.
`r hide("R solution -> dont' peak to early ;) !")`
```{r error = TRUE}
# Recode conti to French.
# Watch out: first the new, then the old value...
conti <- fct_recode(conti, 
                    "Afrika" = "Africa",
                    "Asien" = "Asia",
                    "Australien" = "Australia",
                    "Europa" = "Europe",
                    "Nordamerika" = "N.America",
                    "Suedmerika" = "S.America") 

table(conti)
```
`r unhide()`

3. Use `forcats` functionality to add Atlantis as another level. If you don't know where to start, check out the `forcats` cheat sheet [here](https://raw.githubusercontent.com/rstudio/cheatsheets/master/factors.pdf). To do this, we need the `r fitb("fct_expand()", width = "12")` function.
`r hide("R solution -> dont' peak to early ;) !")`
```{r error = TRUE}
conti <- fct_expand(conti, "Atlantis")

table(conti)
```  
`r unhide()`

4. Reorder the factor vector such, that Atlantis is shown first. Now we need the `r fitb("fct_relevel()", width = "13")` function.
`r hide("R solution -> dont' peak to early ;) !")`
```{r error = TRUE}
conti <- fct_relevel(conti, "Atlantis")

table(conti)
```  
`r unhide()`

5. Import the ESS round 10 data.
`r hide("R solution -> dont' peak to early ;) !")`
```{r eval = FALSE}
# Add packages to library
library(tidyverse) # Add the tidyverse package to my current library.
library(haven) # Handle labelled data.

# Import the ESS round 10
ESS <- read_spss("ESS10.sav")
```

```{r include = FALSE}
# Add packages to library
library(tidyverse) # Add the tidyverse package to my current library.
library(haven) # Handle labelled data.

# Import the ESS round 10
ESS <- read_spss("./../../assets/ESS10.sav")
```
`r unhide()`

6. Keep only a person and a country identifier, `eduyrs`, `agea`, `dscrgrp`, and three variables indicating homophobia `freehms`, `hmsfmlsh`, `hmsacld.` The function that allows you to do that is called `r fitb("select()", width = "8")`.
`r hide("R solution -> dont' peak to early ;) !")`
```{r}
(ESS <- select(ESS, idno, cntry, eduyrs, agea, dscrgrp, 
               freehms, hmsfmlsh, hmsacld))
```
`r unhide()`

7. Change the variables into numeric and factors appropriately. For that, you need the two functions `r fitb("zap_labels()", width = "12")` for numeric and `r fitb("as_factor()", width = "11")` for categorical variables. Also use `fct_drop()` to drop factor levels from `ctnry` that have no observations yet.
`r hide("R solution -> dont' peak to early ;) !")`
```{r}
ESS <- mutate(ESS,
              idno = zap_labels(idno),
              cntry = as_factor(cntry),
              eduyrs = zap_labels(eduyrs),
              agea = zap_labels(agea),
              dscrgrp = as_factor(dscrgrp),
              freehms = zap_labels(freehms),
              hmsfmlsh = zap_labels(hmsfmlsh),
              hmsacld = zap_labels(hmsacld)
)
```
`r unhide()`

8. Top code `eduyrs` to maximum 21 and bottom code it to minimum 9 years. Then recode `dscrgrp` to "Yes" for all persons older than 80 in Bulgaria, and to "No" for all respondents with more than average years of education in France. Use the `table()` function to show the frequency of `dscrgrp` by country. After the recode, `r fitb("324", width = "3")` respondents from Bulgaria answered that they belong to a discriminated minority, and `r fitb("136", width = "3")` from France.
`r hide("R solution -> dont' peak to early ;) !")`
```{r error = TRUE}
ESS <- mutate(ESS,
              # Recode to max 21 years of edu.
              eduyrs = case_when(
                eduyrs > 21 ~ 21,
                eduyrs < 9 ~ 9,
                TRUE ~ as.numeric(eduyrs)
              ),
              dscrgrp = case_when( # Start complex recode
                # Older than 80 & Germany ~ "Yes",
                agea > 80 & cntry == "Bulgaria" ~ "Yes", 
                # Older than mean & France
                eduyrs > mean(eduyrs, na.rm = TRUE) & cntry == "France" ~ "No",
                # All others ~ as before, need to make it character for type consistency.
                TRUE ~ as.character(dscrgrp) 
              ),
              # Now make it a factor again.
              dscrgrp = factor(dscrgrp) 
)

# ... don't forget to check your recode for bugs!

# Absolute frequencies cross-table.
table(ESS$dscrgrp, ESS$cntry) # Israel, no surprise 20% are Arab in this contested state.
```
`r unhide()`

9. Now check out `prop.table()` and find out how to use it. In which country is the share of people reporting that they belong to a discriminated minority the highest?

`r mcq(c("Czechia followed by Croatia", "Croatia followed by Hungary", answer = "Bulgaria followed by Finland", "Hungary followed by Bulgaria"))`

`r hide("R solution -> dont' peak to early ;) !")`
```{r}
# Relative frequencies cross-table.
prop.table(table(ESS$dscrgrp, ESS$cntry), margin = 2) # Relative frequencies.
```
`r unhide()`

10. Show the frequency table only for respondents who are older than 45.
`r hide("R solution -> dont' peak to early ;) !")`
```{r error = TRUE}
# Use the index to select cases
prop.table(table(ESS$cntry[ESS$agea > 45], ESS$dscrgrp))

# You need to make sure to select the same cases for both variables!
prop.table(table(ESS$cntry[ESS$agea > 45], ESS$dscrgrp[ESS$agea > 45]))
```
`r unhide()`

11. How did you filter the cases; would there have been another way?
`r hide("R solution -> dont' peak to early ;) !")`
```{r error = TRUE}
# Use filter() to generate a new tibble that contains only cases who are older than 45.
ESS_46Plus <- filter(ESS, agea > 45)

prop.table(table(ESS_46Plus$cntry, ESS_46Plus$dscrgrp))
```
`r unhide()`

