---
title: "Web Exercise 2"
author: Merlin Schaeffer
output: webex::webex_default
date: 2021-02-08
publishdate: 2021-01-25
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE, servr.interval = 0.5, width = 115, digits = 2)
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, 
  warning = FALSE, cache = FALSE,
  comment = "#", strip.white = TRUE)

library(webex)
library(tidyverse)

options(htmltools.dir.version = FALSE, servr.interval = 0.5, width = 115, digits = 2)
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, 
  warning = FALSE, cache = FALSE,
  comment = "#", strip.white = TRUE)

# Concatenate argument "x" to a factor and give it a
# comprehensive list "levels" of all potential categories.
conti <- factor(
  x = c("Europe", "Africa", "Africa", "Asia", "S.America"),
  levels = c("Africa", "Asia", "Australia",
             "Europe", "N.America", "S.America")
)

# Recode conti to Danish. Watch out: first the new, then the old value...
conti <- fct_recode(conti,
                    "Europa" = "Europe",
                    "Afrika" = "Africa",
                    "Asien" = "Asia",
                    "Suedamerika" = "S. America",
                    "Nordamerika" = "N. America",
                    "Australien" = "Australia") 

conti <- fct_drop(conti) # Drop unused levels.
```


1. Create numeric vector that runs from 1 to 10 and let R print it. To create and print it right away, you need to enclose your statement with `r fitb("()", width = "2")`.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
(my_numeric_vector <-seq(1, 10))
```
`r unhide()`

2. Now transform that vector so that it's 8th element is being multiplied by 4 and add 7 to it's second element. To access single elements of a vector, you need to use its index via `r fitb("[]", width = "2")`.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
my_numeric_vector[c(8, 2)] <- c(my_numeric_vector[8] * 4, 
                                my_numeric_vector[2] + 7)

my_numeric_vector
```
`r unhide()`

3. Recode the continent variable into your language, or back to English. To do that, we use the `r fitb("fct_recode()", width = "10")` function from the forcats package.
`r hide("R solution -> dont' peek to early ;) !")`
```{r error = TRUE}
# Recode conti to French.
# Watch out: first the new, then the old value...
conti <- fct_recode(conti, 
                    "Europe" = "Europa", 
                    "Afrique" = "Afrika", 
                    "Asie" = "Asien", 
                    "Amérique Sud" = "Suedamerika") 

table(conti)
```
`r unhide()`

4. Add Atlantis as another level. Now we need the `r fitb("fct_expand()", width = "12")` function.
`r hide("R solution -> dont' peek to early ;) !")`
```{r error = TRUE}
conti <- fct_expand(conti, "Atlantis")

table(conti)
```  
`r unhide()`

5. Reorder the factor vector such, that Atlantis is shown first. Now we need the `r fitb("fct_relevel()", width = "13")` function.
`r hide("R solution -> dont' peek to early ;) !")`
```{r error = TRUE}
conti <- fct_relevel(conti, "Atlantis")

table(conti)
```  
`r unhide()`


