---
title: "Web Exercise 1"
author: Merlin Schaeffer & Friedolin Merhout
output: webexercises::webexercises_default
date: 2021-10-18
publishdate: 2021-01-25
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE, servr.interval = 0.5, width = 115, digits = 2)
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, 
  warning = FALSE, cache = FALSE,
  comment = "#", strip.white = TRUE)

library(webexercises)
library(tidyverse)

options(htmltools.dir.version = FALSE, servr.interval = 0.5, width = 115, digits = 2)
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, 
  warning = FALSE, cache = FALSE,
  comment = "#", strip.white = TRUE)

# Concatenate argument "x" to a factor and give it a
# comprehensive list "levels" of all potential categories.
conti <- factor(
  x = c("Europe", "Africa", "Africa", "Asia", "S.America"),
  levels = c("Africa", "Asia", "Australia",
             "Europe", "N.America", "S.America")
)

# Recode conti to Danish. Watch out: first the new, then the old value...
conti <- fct_recode(conti,
                    "Europa" = "Europe",
                    "Afrika" = "Africa",
                    "Asien" = "Asia",
                    "Suedamerika" = "S. America",
                    "Nordamerika" = "N. America",
                    "Australien" = "Australia") 

conti <- fct_drop(conti) # Drop unused levels.
```

To work on these exercises, it is best you create a new R Script "Exercise1.R" that contains your solutions, so you don't intermix exercises with lecture notes.

1. Why does the code below throw an error? Explain, and then solve the problem.
```{r error = TRUE}
Oh_a_new_object <- 10
0h_a_new_object
```
`r hide("R solution -> dont' peak to early ;) !")`
```{r}
Oh_a_new_object <- 10
Oh_a_new_object # Exchange the number 0 for the letter O #<<
```
`r unhide()`

2. Create an object `another_object2` that contains whole numbers from 123 to 131. The name of the function allowing you to do that is: `r fitb("seq()", width = "5")` and the assignment operator that creates the object is `r fitb("<-", width = "2")`.
`r hide("R solution -> dont' peak to early ;) !")`
```{r}
(another_object2 <- seq(123, 131))
```
`r unhide()`

3. Let R evaluate which of `another_object2`'s elements is larger than 128 and smaller than 130.
`r hide("R solution -> dont' peak to early ;) !")`
```{r}
another_object2 > 128 & another_object2 < 130
```
`r unhide()`

4. Add 2 to each element of another_object2 and check again which of its elements is larger than 128 and smaller than 130.
`r hide("R solution -> dont' peak to early ;) !")`
```{r}
another_object2 <- another_object2 + 2
another_object2 > 128 & another_object2 < 130
```
`r unhide()`

5. Create an object `another_textobject` that contains the sentence: "I am just another sentence."
`r hide("R solution -> dont' peak to early ;) !")`
```{r}
(another_textobject <- "I am just another sentence.")
```
`r unhide()`

6. What does R return if you try to multiply `another_textobject` by 3?
```{r echo = FALSE}
another_textobject <- "I am just another sentence."
```
`r mcq(c(answer = "non-numeric argument to binary operator", "type mismatch", "'I am just another sentence.' 'I am just another sentence.' 'I am just another sentence.'"))`
`r hide("R solution -> dont' peak to early ;) !")`
```{r error = TRUE}
another_textobject <- another_textobject * 3
```
`r unhide()`

7. Use the `rep()` function to repeat `another_textobject` five times. The argument to which you need to supply the value 5 is called `r fitb("times", width = "5")`.
`r hide("R solution -> dont' peak to early ;) !")`
```{r}
rep(another_textobject, times = 5)
```
`r unhide()`

8. Use the `rep()` function to repeat `another_object2` three times and assign it to a new object called `another_object2_triple`. Then use the `length()` function to find out the number of elements in the object. How many are there? `r fitb("27", width = "2")`
`r hide("R solution -> dont' peak to early ;) !")`
```{r}
another_object2_triple <- rep(another_object2, times = 3)

length(another_object2_triple)
```
`r unhide()`

9. Use the `rep()` function to repeat *each element* of `another_object2` three times. The argument to which you need to supply the value 3 is called `r fitb("each", width = "4")`.
`r hide("R solution -> dont' peak to early ;) !")`
```{r}
rep(another_object2, each = 3)
```
`r unhide()`

10. Create a numeric vector that runs from 1 to 10 and let R print it. To create and print it right away, you need to enclose your statement with `r fitb("()", width = "2")`.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
(my_numeric_vector <-seq(1, 10))
```
`r unhide()`

11. Now access the 8th element of the vector you just created and multiply it by 4. Then, access the 2nd element and add 7 to it. To access single elements of a vector, you need to use its index via `r fitb("[]", width = "2")`. _Bonus:_ Can you assign these processed values to their respective place in the vector?
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
my_numeric_vector[8] * 4 
my_numeric_vector[2] + 7 

my_numeric_vector[8] <- my_numeric_vector[8] * 4 
my_numeric_vector[2] <- my_numeric_vector[2] + 7 

my_numeric_vector
```
`r unhide()`