---
title: "Web Exercise 9"
author: Merlin Schaeffer
output: webex::webex_default
date: 2020-03-03
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE, servr.interval = 0.5, width = 115, digits = 2)
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, 
  warning = FALSE, cache = FALSE,
  comment = "#", strip.white = TRUE)

library(webex)
```

1) Use today's set-up; the tibble has `r fitb("5561", width = "4")` observations.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
# Add packages to library
library(tidyverse) # Add the tidyverse package to my current library.
library(haven) # Handle labelled data.
library(essurvey) # Add ESS API package.
library(ggplot2) # Allows us to create nice figures.
library(factoextra) # Allows us to visualize PCAs
library(psych) # Supports PCA & factor analysis with several useful functions.
library(estimatr) # Allows us to estimate (cluster-)robust standard errors
library(texreg) # Allows us to make nicely-formatted Html & Latex regression tables.
library(broom) # Allows us to turn parts of model objects into tibbles.
```

```{r include = FALSE}
# Import the ESS round 9 data via the API
ESS <- import_rounds(rounds = 9, ess_email = "merlin.schaeffer@uni-koeln.de", format = "spss")
```

```{r}
ESS <- ESS %>% transmute( # Create new variables and keep only those
    cntry = as_factor(cntry), # Country of interview
    gndr = as_factor(gndr),
    facntr = as_factor(facntr), # Father born in cntry
    mocntr = as_factor(mocntr), # Mother born in cntry
    imbgeco = max(imbgeco, na.rm = TRUE) - zap_labels(imbgeco),
    imueclt = max(imueclt, na.rm = TRUE) - zap_labels(imueclt),
    imwbcnt = max(imwbcnt, na.rm = TRUE) - zap_labels(imwbcnt),
    # Regigion
    rlgblg = as_factor(rlgblg), # Belonging to a religion
    rlgdgr = zap_labels(rlgdgr), # How religios
    rlgatnd = max(rlgatnd, na.rm = TRUE) - zap_labels(rlgatnd), # Service attendance
    pray = max(pray, na.rm = TRUE) - zap_labels(pray), # Prayer frequency
    pspwght = zap_label(pspwght),
    # Parental education (ISCED) #<<
    eiscedf = zap_labels(eiscedf), #<<
    eiscedm = zap_labels(eiscedm), #<<
    par_edu = case_when( #<<
      # If father's edu is missing but not mother's, take mother's #<<
      (eiscedf == 55 | is.na(eiscedf)) & eiscedm != 55 & !is.na(eiscedm) ~ eiscedm, #<<
      # If mother's edu is missing but not father's, take father's #<<
      (eiscedm == 55 | is.na(eiscedm)) & eiscedf != 55 & !is.na(eiscedf)  ~ eiscedf, #<<
      # If both are missing, its missing #<<
      eiscedf == 55 & eiscedm == 55 ~ as.numeric(NA), #<<
      # For all others, take the average of both parents #<<
      TRUE ~ (eiscedm + eiscedf) / 2), #<<
    eduyrs = case_when( # Education
      eduyrs > 21 ~ 21, # Recode to max 21 years of edu.
      eduyrs < 9 ~ 9, # Recode to min 9 years of edu.
      TRUE ~ zap_labels(eduyrs))) %>% # Make it numeric, then
  dplyr::filter(
    # Keep only respondents with native-born parents,
    facntr == "Yes" & mocntr == "Yes" &
      (cntry == "Denmark" | cntry == "Sweden" | cntry == "Norway" | cntry == "Germany"))
```
`r unhide()`

2) Among these religious respondents, the ESS contains three questions on religiosity: Prayer frequency, attendance of religious services, and general importance. Use PCA to identify a xenophobia and a religiosity variable. Using oblique rotation, the two correlate by r = `r fitb("-0.0017", width = "7")`.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
# Conduct PCA of climate change concerns
(pca <- ESS %>% prcomp(
  formula = ~ imbgeco + imueclt + imwbcnt + 
    rlgdgr + rlgatnd + pray,
  data = ., na.action = na.exclude,
  center = TRUE, scale = TRUE))

# Show importance of single components.
summary(pca) 

# Oblique rotation
(oblique_solution <- promax(
  # of first two PCs
  pca$rotation[, c("PC1", "PC2")]))

# Visualize the results
pca$rotation <- oblique_solution$loadings
fviz_pca_var(pca, # Visualize PCA object
             # Color by contributions to the PC
             col.var = "contrib",
             # From blue to red.
             gradient.cols = c(low = "#00AFBB", 
                               mid = "#E7B800", 
                               high = "#FC4E07"))

# Generate new component scores for every respondent based on the 
# rotated principal components and write the into object "rotated_PCs"
rotated_PCs <- ESS %>% 
  dplyr::select(imbgeco, imueclt, imwbcnt, 
    rlgdgr, rlgatnd, pray) %>% 
  factor.scores(x = ., f = pca$rotation)
# Add a "xeno" and "relig" from "rotated_PCs" to our data.
ESS[, c("xeno", "relig")] <- rotated_PCs$scores

# Correlation
ESS %>%
  select(xeno, relig) %>%
  drop_na() %>%
  cor()
```
`r unhide()`

3) Model 1: Regress xenophobia on religiosity; $\beta$ = `r fitb("0.00368", width = "7")` and the relation is `r mcq(c("Significant", answer = "Insignificant"))`
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
ols1 <- lm_robust(xeno ~ relig, w = pspwght, data = ESS)
summary(ols1)
```
`r unhide()`

4) Model 2: Add `cntry`, `par_edu`, `eduyrs`, and `gndr` as control variables, what happens to our religiosity estimate? `r mcq(c("It does not change", "It turns more negative and actually becomes significant", "It turns significantly positive", answer = "It turns positive but remains insignificant", "It remains insignificantly negative"))`
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
ols2 <- lm_robust(xeno ~ relig + eduyrs + par_edu + cntry + gndr, w = pspwght, data = ESS)
summary(ols2)
```
`r unhide()`

5) Make Denmark the refernce category (i.e., the first category) in the `cntry` variable.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
ESS$cntry <- fct_relevel(ESS$cntry, "Denmark")
```
`r unhide()`

6) Estimate Model 2 again. What changed? Discuss among each other.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
ols2 <- lm_robust(xeno ~ relig + eduyrs + par_edu + cntry + gndr, w = pspwght, data = ESS)
summary(ols2)
```
`r unhide()`

7) Make a regression table of the results of Models 1 and (the revised) 2.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
screenreg(list(ols1, ols2), include.ci = FALSE,
          custom.coef.names = c("Intercept", 
                                "Religiosity",
                                "Years of education",
                                "Parental education", 
                                "Germany", "Norway", "Sweden", 
                                "Women"),
          caption = "My regression table", 
          caption.above = TRUE)
```
`r unhide()`

6) Make a coefficient plot of the results of Model 1 and 2, and emphasize religiosity as predictor of interest.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
bind_rows(tidy(ols1), tidy(ols2), # Stack the data of model objects into one tibble.
          .id = "model") %>% # Identify which model the data came from, then
  mutate(
    model = case_when(model == 1 ~ "Model 1", # Rename model identifyer.
                      model == 2 ~ "Model 2"),
    term = fct_recode(factor(term), # Recode predictor names, then
                      "Intercept" = "(Intercept)",
                      "Religiosity" = "relig",
                      "Years of Education" = "eduyrs",
                      "Parental education" = "par_edu",
                      "Germany" = "cntryGermany",
                      "Norway" = "cntryNorway",
                      "Sweden" = "cntrySweden",
                      "Women" = "gndrFemale")) %>% 
  select(term, estimate, conf.low, conf.high, model) %>% # keep only some of all the info, then
  ggplot(aes(x = reorder(term, estimate),
             y = estimate, 
             ymin = conf.low, ymax = conf.high,
             color = model)) +
  geom_hline(yintercept = 0, # Null-hypothesis line.
             color = "#901A1E", lty = "dashed") + 
  geom_pointrange(# Coefs & 95% CI. #<<
    position = position_dodge(width=0.5)) + #<<
  coord_flip() + 
  theme_minimal() +
  labs(y = expression(beta), # Axis title: greek beta.
       x = "") +
  theme(legend.position="bottom",
        legend.title=element_blank(),
        legend.box = 'vertical')
```
`r unhide()`

7) Drop the two intercepts and the Sweden dummy from the coefficients plot, but mention this in the plot's caption.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
bind_rows(tidy(ols1), tidy(ols2), # Stack the data of model objects into one tibble.
          .id = "model") %>% # Identify which model the data came from, then
  dplyr::filter(term != "(Intercept)" & term != "cntrySweden") %>% # drop the two intercepts and Sweden dummy, then
  mutate(
    model = case_when(model == 1 ~ "Model 1", # Rename model identifyer.
                      model == 2 ~ "Model 2"),
    term = fct_recode(factor(term), # Recode predictor names, then
                      "Religiosity" = "relig",
                      "Years of Education" = "eduyrs",
                      "Parental education" = "par_edu",
                      "Germany" = "cntryGermany",
                      "Norway" = "cntryNorway",
                      "Sweden" = "cntrySweden",
                      "Women" = "gndrFemale")) %>% 
  select(term, estimate, conf.low, conf.high, model) %>% # keep only some of all the info, then
  ggplot(aes(x = reorder(term, estimate),
             y = estimate, 
             ymin = conf.low, ymax = conf.high,
             color = model)) +
  geom_hline(yintercept = 0, # Null-hypothesis line.
             color = "#901A1E", lty = "dashed") + 
  geom_pointrange(# Coefs & 95% CI. #<<
    position = position_dodge(width=0.5)) + #<<
  coord_flip() + 
  theme_minimal() +
  labs(y = expression(beta), # Axis title: greek beta.
       x = "",
       caption = "(Estimates of the intercept are not shown)") +
  theme(legend.position="bottom",
        legend.title=element_blank(),
        legend.box = 'vertical')
```
`r unhide()`
