---
title: "Web Exercise 8"
author: Merlin Schaeffer & Friedolin Merhout
output: webexercises::webexercises_default
date: 2022-10-21
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE, servr.interval = 0.5, width = 115, digits = 2)
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, 
  warning = FALSE, cache = FALSE,
  comment = "#", strip.white = TRUE)

library(webexercises)
```

1) Use the set-up from our OLS II slides but add variables on religiosity: `rlgblg`, `rlgdgr`, `rlgatnd`, `pray`. Specifically, among religious respondents, the ESS contains three questions on their degree of religiosity: Prayer frequency, attendance of religious services, and general importance of religion. Be a cheat and assign the non-religious the minimum value on each of these three variables. Also make sure that larger values indicate higher religiosity. The tibble has `r fitb("5817", width = "4")` observations.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
# Add packages to library
library(tidyverse) # Add the tidyverse package to my current library.
library(haven) # Handle labelled data.
library(ggplot2) # Allows us to create nice figures.
library(estimatr) # Allows us to estimate (cluster-)robust standard errors
library(texreg) # Allows us to make nicely-formatted Html & Latex regression tables.
library(broom) # Allows us to turn parts of model objects into tibbles.
```

```{r include = FALSE}
# Load the previously downloaded ESS round 10 data
ESS <- read_spss("./../../assets/ESS10.sav")
```

```{r}
ESS <- ESS %>% transmute( # Create new variables and keep only those
    cntry = as_factor(cntry) %>% fct_relevel("France"), # Country of interview #<<
    gndr = as_factor(gndr), # Gender
    agea = zap_labels(agea), # Age
    facntr = as_factor(facntr), # Father born in cntry
    mocntr = as_factor(mocntr), # Mother born in cntry
    imwbcnt = max(imwbcnt, na.rm = TRUE) - zap_labels(imwbcnt), # Immigrants make country better (0) - worse (10) place
    nwspol_hrs = zap_labels(ESS$nwspol)/60, # Daily political news consumption in hours #<<
    rtrd = as_factor(rtrd), # Last 7 days: retired #<<
    # Religion
    rlgblg = as_factor(rlgblg), # Belonging to a religion
    rlgdgr = case_when( # How religious
      rlgblg == "No" ~ 0,
      TRUE ~ zap_labels(rlgdgr)),
    rlgatnd = case_when( # Service attendance
      rlgblg == "No" ~ 0,
      TRUE ~ max(rlgatnd, na.rm = TRUE) - zap_labels(rlgatnd)),
    pray = case_when( # Prayer frequency
      rlgblg == "No" ~ 0,
      TRUE ~ max(pray, na.rm = TRUE) - zap_labels(pray)),
    pspwght = pweight*dweight,
    eduyrs = case_when( # Education
      eduyrs > 21 ~ 21, # Recode to max 21 years of edu.
      eduyrs < 9 ~ 9, # Recode to min 9 years of edu.
      TRUE ~ zap_labels(eduyrs))) %>% # Make it numeric, then
  dplyr::filter( # Keep only respondents with native-born parents in four countries
    facntr == "Yes" & mocntr == "Yes",
    cntry %in% c("France", "Estonia", "Finland", "Hungary"))
  
```
`r unhide()`

2) Model 1: Regress xenophobia (i.e., `imwbcnt`) on the importance of religion (i.e., `rlgdgr`); $\beta$ = `r fitb("0.042", width = "7")` and the relation is statistically `r mcq(c("Insignificant", "Interesting", "Important", answer = "Significant"))`.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
ols1 <- lm_robust(imwbcnt ~ rlgdgr, w = pspwght, data = ESS)
summary(ols1)
```
`r unhide()`

2) Model 2: Add religious service attendance to the model. The $\beta$ for importance of religion is now `r fitb("0.0335", width = "7")` and the relation is statistically `r mcq(c("Significant", "Interesting", "Important", answer = "Insignificant"))`.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
ols2 <- lm_robust(imwbcnt ~ rlgdgr + rlgatnd, w = pspwght, data = ESS)
summary(ols2)
```
`r unhide()`

4) Model 3: Add `cntry`, `agea`, `eduyrs`, and `gndr` as control variables, what happens to our religiosity estimates? `r mcq(c("They do not change", "They both turn negative", "They both turn positive and significant", answer = "They both half in size and remain insignificant"))`
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
ols3 <- lm_robust(imwbcnt ~ rlgdgr + rlgatnd + eduyrs + agea + cntry + gndr, w = pspwght, data = ESS)
summary(ols3)
```
`r unhide()`

5) Make Finland the reference category (i.e., the first category) in the `cntry` variable.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
ESS$cntry <- fct_relevel(ESS$cntry, "Finland")
```
`r unhide()`

6) Re-estimate Model 3. What changed and why? Discuss among each other.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
ols3 <- lm_robust(imwbcnt ~ rlgdgr + rlgatnd + eduyrs + agea + cntry + gndr, w = pspwght, data = ESS)
summary(ols3)
```
`r unhide()`

7) Make a regression table of all three models with labelled coefficients.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
screenreg(list(ols1, ols2, ols3), include.ci = FALSE,
          custom.coef.names = c("Intercept", 
                                "Importance of religion",
                                "Frequency of religious service attendance",
                                "Years of education",
                                "Parental education", 
                                "France", "Estonia", "Hungary",
                                "Women"),
          caption = "My regression table", 
          caption.above = TRUE)
```
`r unhide()`

6) Make a coefficient plot of the results of Model 2 and 3, and emphasize the two religiosity variables as predictors of interest.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
bind_rows(tidy(ols2), tidy(ols3), # Stack the data of model objects into one tibble.
          .id = "model") %>% # Identify which model the data came from, then
  mutate(
    model = case_when(model == 1 ~ "Model 1", # Rename model identifyer.
                      model == 2 ~ "Model 2"),
    term = fct_recode(factor(term), # Recode predictor names, then
                      "Intercept" = "(Intercept)",
                      "Importance of religion" = "rlgdgr",
                      "Frequency of religious service attendance" = "rlgatnd",
                      "Years of Education" = "eduyrs",
                      "Parental education" = "par_edu",
                      "France" = "cntryFrance",
                      "Estonia" = "cntryEstonia",
                      "Hungary" = "cntryHungary",
                      "Women" = "gndrFemale"),
    predictor = case_when(
      term %in% c("Importance of religion", "Frequency of religious service attendance") ~ "Predictor",
      TRUE ~ "Potential confounder")) %>% 
  select(term, estimate, conf.low, conf.high, model, predictor) %>% # keep only relevant info, then
  ggplot(aes(x = reorder(term, estimate),
             y = estimate, 
             ymin = conf.low, ymax = conf.high,
             shape = model,
             color = predictor)) +
  geom_hline(yintercept = 0, # Null-hypothesis line.
             color = "#901A1E", lty = "dashed") + 
  geom_pointrange(# Coefs & 95% CI. #<<
    position = position_dodge(width=0.5)) + #<<
  coord_flip() + 
  theme_minimal() +
  labs(y = expression(beta), # Axis title: greek beta.
       x = "") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        legend.box = 'vertical')
```
`r unhide()`

7) Drop the two intercepts and the France dummy from the coefficients plot (for no good reason really ;)), but mention this in the plot's caption.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
bind_rows(tidy(ols2), tidy(ols3), # Stack the data of model objects into one tibble.
          .id = "model") %>% # Identify which model the data came from, then
  dplyr::filter(term != "(Intercept)" & term != "cntryFrance") %>% # drop the two intercepts and Sweden dummy, then
  mutate(
    model = case_when(model == 1 ~ "Model 1", # Rename model identifyer.
                      model == 2 ~ "Model 2"),
    term = fct_recode(factor(term), # Recode predictor names, then
                      "Importance of religion" = "rlgdgr",
                      "Frequency of religious service attendance" = "rlgatnd",
                      "Years of Education" = "eduyrs",
                      "Parental education" = "par_edu",
                      "Estonia" = "cntryEstonia",
                      "Hungary" = "cntryHungary",
                      "Women" = "gndrFemale"),
    predictor = case_when(
      term == "Importance of religion" | 
        term == "Frequency of religious service attendance" ~ "Predictor",
      TRUE ~ "Potential confounder")) %>% 
  select(term, estimate, conf.low, conf.high, model, predictor) %>% # keep only some of all the info, then
  ggplot(aes(x = reorder(term, estimate),
             y = estimate, 
             ymin = conf.low, ymax = conf.high,
             shape = model, 
             color = predictor)) +
  geom_hline(yintercept = 0, # Null-hypothesis line.
             color = "#901A1E", lty = "dashed") + 
  geom_pointrange(# Coefs & 95% CI. #<<
    position = position_dodge(width = 0.5)) + #<<
  coord_flip() + 
  theme_minimal() +
  labs(y = expression(beta), # Axis title: greek beta.
       x = "",
       caption = "(Estimates of the intercept and a France dummy are not shown)") +
  theme(legend.position="bottom",
        legend.title=element_blank(),
        legend.box = 'vertical')
```
`r unhide()`
