---
title: "Web Exercise 7"
author: Merlin Schaeffer & Friedolin Merhout
output: webexercises::webexercises_default
date: 2022-10-21
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE, servr.interval = 0.5, width = 115, digits = 2)
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, 
  warning = FALSE, cache = FALSE,
  comment = "#", strip.white = TRUE)

library(webexercises)
library(essentials)
```

1) Use the set-up from our OLS I slides but instead of `imwbcnt` and `eduyrs`, add the following variables: `agea`, `gndr`, `rlgdgr`. Check whether larger values on `rlgdgr` indicate higher religiosity. Only keep complete cases by using `drop_na()`. The tibble has `r fitb("6185", width = "4")` observations.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
# Add packages to library
library(tidyverse) # Add the tidyverse package to my current library.
library(haven) # Handle labelled data.
library(ggplot2) # Allows us to create nice figures.
library(estimatr) # Allows us to estimate (cluster-)robust standard errors
library(texreg) # Allows us to make nicely-formatted Html & Latex regression tables.
library(broom) # Allows us to turn parts of model objects into tibbles.
```

```{r include = FALSE}
# Load the previously downloaded ESS round 10 data
ESS <- read_spss("./../../assets/ESS10.sav")
```

```{r}
ESS <- ESS %>% transmute( # Create new variables and keep only those
  idno = zap_labels(idno),
  cntry = as_factor(cntry) %>% fct_drop(), # Country of interview
  facntr = as_factor(facntr), # Father born in cntry
  mocntr = as_factor(mocntr), # Mother born in cntry
  pspwght = dweight*pweight,
  gndr = as_factor(gndr), # Gender
  agea = zap_labels(agea), # Age
  # How religious
  rlgdgr = zap_labels(rlgdgr)) %>% 
  dplyr::filter(
    # Keep only respondents with native-born parents,
    facntr == "Yes" & mocntr == "Yes" &
      (cntry %in% c("Slovakia", "Hungary", "Czechia", "Slovenia"))) %>%
  drop_na() # Keep only complete cases.

nrow(ESS)
```
`r unhide()`

```{r ols1, include = FALSE}
ols1 <- lm_robust(rlgdgr ~ agea, weights = pspwght, data = ESS)
screenreg(ols1, digits = 3, include.ci = FALSE)

coeffer <- as.scalar(coef(ols1)["agea"])
```

2) Regress religiosity on age and make a regression table that displays 3 digits and standard errors in parentheses using `texreg::screenreg()`; $\beta$ = `r fitb(0.05, width = "4")` and the relation is statistically `r mcq(c("Insignificant", "Interesting", "Important", answer = "Significant"))`.
`r hide("R solution -> dont' peek to early ;) !")`
```{r ref.label = "ols1"}
```
`r unhide()`

3) Visualize the implied relationship from year 0 to 100 by using model predictions. Mark the range of observed ages.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
# Make artificial ages.
fict_dat <- tibble(agea = 0:100)

fict_dat <- predict( #<<
  ols1, newdata = fict_dat, #<<
  interval = "confidence", level = 0.95)$fit %>% #<<
  as_tibble() %>% # Turn into a tibble, then
  bind_cols(fict_dat, .) # Add to the synthetic data.

ggplot(data = fict_dat, aes(y = fit, x = agea)) +
  geom_vline(xintercept = c(15, 90), color = "red", lty = "dashed") +
  geom_ribbon(aes(ymin = lwr, ymax = upr), alpha = 0.5) +
  geom_line() +
  labs(
    title = "Predictions based on regression of religiosity",
    x = "By age in years",
    # Write Greek beta into axis title.
    y = "Predicted average of religiosity") +
  theme_minimal()
```
`r unhide()`

```{r ols2, include = FALSE}
ols2 <- lm_robust(rlgdgr ~ gndr, weights = pspwght, data = ESS)
screenreg(ols2, digits = 3, include.ci = FALSE)
```

4) Regress religiosity on gender and make a regression table that displays 3 digits and standard errors in parentheses using `texreg::screenreg()`; $\beta$ = `r fitb(0.792, width = "5")` and the relation is statistically `r mcq(c("Insignificant", "Interesting", "Important", answer = "Significant"))`.
`r hide("R solution -> dont' peek to early ;) !")`
```{r ref.label = "ols2"}
```
`r unhide()`

5) Make a cofficient plot of the result.
`r hide("R solution -> dont' peek to early ;) !")`
```{r Coefplot2, out.width='100%', fig.height = 4, fig.width = 6}
plotdata2 <- ols2 %>%
  tidy() %>% # Turn results into a tibble,
  mutate( # Rename variables for the plot.
    term = case_when(
      term == "gndrFemale" ~ "Women",
      term == "(Intercept)" ~ "Intercept")) %>%
  filter(term != "Intercept")

ggplot(data = plotdata2, aes(y = estimate, 
                            # Order by effect size
                            x = reorder(term, estimate))) +
  geom_hline(yintercept = 0, color = "red", lty = "dashed") +
  # Point with error-bars,
  geom_pointrange(aes(min = conf.low, max = conf.high)) +
  coord_flip() + # Flip Y- & X-Axis,
  labs(
    title = "Regression of religiosity",
    x = "",
    # Write Greek beta into axis title.
    y = "Religiosity as compared to men") +
  theme_minimal()
```
`r unhide()`
