---
title: "Web Exercise 6"
author: Merlin Schaeffer & Friedolin Merhout
output: webexercises::webexercises_default
date: 2021-10-20
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE, servr.interval = 0.5, width = 115, digits = 2)
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, fig.align='center',
  warning = FALSE, cache = FALSE, fig.retina = 3,
  comment = "#", strip.white = TRUE)

# Add packages to library
library(tidyverse) # Add the tidyverse package to my current library.
library(haven) # Handle labelled data.
library(Hmisc) # Weighted statistics
library(webexercises)

# Import the ESS round 10
ESS <- read_spss("./../../assets/ESS10.sav")
```

Session page: [**Visualization III**](#sessions)

1. Remember Exercise 5 from earlier today; visualize your results of task 2 and 3 in one plot each. Color-highlight the most extreme country in each plot. 
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
ESS %>% # Use the ESS, then
  transmute( # Create new variables and only keep these new ones
    # Make the following variables factors:
    cntry = as_factor(cntry) %>% fct_drop(), 
    facntr = as_factor(facntr),
    mocntr = as_factor(mocntr),
    # Make the following variables numeric:
    pspwght = pweight*dweight,
    # Experienced racial discrimination #<<
    # Turn vars into factors:
    dscrgrp = as_factor(dscrgrp), # Belonging to discriminated group.
    dscrrce = as_factor(dscrrce), # Discriminated because of race.
    racial_discr = case_when(
      dscrgrp == "Yes" & dscrrce == "Marked" ~ 1, # Only racial discrimination counts as 1 #<<
      dscrgrp == "No" | (dscrgrp == "Yes" & dscrrce != "Marked") ~ 0, # No, or all other forms of discr. count as 0 #<<
      TRUE ~ as.numeric(NA) # all others missing
    ) 
  ) %>% # then
  dplyr::filter( # Keep only respondents of immigrant origin,
    facntr == "No" & mocntr == "No") %>% # then
  group_by(cntry) %>% # Group data by country, then
  dplyr::summarize(
    # Weighted number of cases.
    wn = sum(pspwght, na.rm = TRUE), 
    # Weighted number of persons who see their group face racial discrimination.
    wn_rd = sum(racial_discr * pspwght, na.rm = TRUE), 
    # Weighted percent who see their group face racial discrimination.
    wperc_rd = (wn_rd / wn)  * 100 
  ) %>%
  mutate(
    maxim = case_when(wperc_rd == max(wperc_rd) ~ "Maximum",
                      TRUE ~ "Other")) %>%
  ggplot(mapping = aes(y = wperc_rd, x = reorder(cntry, -wperc_rd))) + 
  geom_bar(aes(fill = maxim), stat = "identity") +
  labs(y = "% Persons of immigrant origin \n reporting racial discrimination",
       x = "Country",
       fill = "Level of Discrimination") +
  coord_flip() +
  theme_minimal() +
  theme(legend.position = c(0.87, 0.87),
        legend.background = 
          element_rect(fill = NA,
                       color = NA))
```
`r unhide()`

2. Use another way (apart from color) to also emphasize, the *least* extreme case in plot two.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
ESS %>% # Use the ESS, then
  transmute( # Create new variables and only keep these new ones
    # Make the following variables factors:
    cntry = as_factor(cntry) %>% fct_drop(), 
    # Make the following variables numeric:
    pspwght = pweight*dweight,
    hmsacld = max(zap_labels(hmsacld), na.rm = TRUE) - zap_labels(hmsacld),
  ) %>%
  group_by(cntry) %>% # Group data by country, så
  dplyr::summarize(
    n = sum(pspwght, na.rm = TRUE),
    mean_hmsacld = wtd.mean(hmsacld, weights = pspwght, na.rm = TRUE),
    sd_hmsacld = wtd.var(hmsacld, weights = pspwght, na.rm = TRUE) %>% sqrt(),
    se_hmsacld = sd_hmsacld / sqrt(n),
    min95 = mean_hmsacld - se_hmsacld * qt(p = 0.975, df = n),
    max95 = mean_hmsacld + se_hmsacld * qt(p = 0.975, df = n)
  ) %>%
  mutate(maxim = case_when(mean_hmsacld == max(mean_hmsacld) ~ "Maximum", #<<
                           TRUE ~ "Other"),
         minim = case_when(mean_hmsacld == min(mean_hmsacld) ~ "Minimum", #<<
                           TRUE ~ "Other")) %>%
  ggplot(aes(y = mean_hmsacld, x = reorder(cntry, mean_hmsacld), 
             ymin = min95, ymax = max95,
             color = maxim, shape = minim)) + #<<
  geom_pointrange() +
  coord_flip() +
  labs(y = "Gay men and women should be allowed \n to adopt children (Scale 1 to 5)",
       x = "Country",
       color = "Level of Discrimination",
       shape = "Level of Discrimination") +
  theme_minimal()
```
`r unhide()`

3. Polish your favorite figure and share it in the chat.
