---
title: "Web Exercise 5"
author: Merlin Schaeffer & Friedolin Merhout
output: webexercises::webexercises_default
date: 2021-10-20
publishdate: 2021-01-15
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE, servr.interval = 0.5, width = 115, digits = 2)
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, fig.align = 'center',
  warning = FALSE, cache = FALSE, fig.retina = 3,
  comment = "#", strip.white = TRUE)

# Add packages to library
library(tidyverse) # Add the tidyverse package to my current library.
library(haven) # Handle labelled data.
library(Hmisc) # Weighted statistics
library(webexercises)

# Import the ESS round 10
ESS <- read_spss("./../../assets/ESS10.sav")
```

1. Rewrite the following code chunks using the `%>%` operator.
  + `log(sd(c(5, 13, 89)))`
  + `as.numeric(scale(c(100, 32, 45)))`
  
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
log(sd(c(5, 13, 89)))
c(5, 13, 89) %>% sd() %>% log()

as.numeric(scale(c(100, 32, 45)))
c(100, 32, 45) %>% scale() %>% as.numeric()
```
`r unhide()`

2. In which among **all** ESS countries is perceived *racial* discrimination among persons of immigrant origin (i.e., persons born abroad or with at least one parent who was born abroad) most prevalent? `r fitb("Slovakia", width = "14")`
    + That is, give a country-level summary of the percent of immigrant minority respondents who experienced discrimination explicitly based on their group's race. 
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
ESS %>% # Use the ESS, then
  transmute( # Create new variables and only keep these new ones
    # Make the following variables factors:
    cntry = as_factor(cntry) %>% fct_drop(), 
    facntr = as_factor(facntr),
    mocntr = as_factor(mocntr),
    # Make the following variables numeric:
    pspwght = dweight*pweight,
    # Experienced racial discrimination #<<
    # Turn vars into factors:
    dscrgrp = as_factor(dscrgrp), # Belonging to discriminated group.
    dscrrce = as_factor(dscrrce), # Discriminated because of race.
    racial_discr = case_when(
      dscrgrp == "Yes" & dscrrce == "Marked" ~ 1, # Only racial discrimination counts as 1 #<<
      dscrgrp == "No" | (dscrgrp == "Yes" & dscrrce != "Marked") ~ 0, # No, or all other forms of discr. count as 0 #<<
      TRUE ~ as.numeric(NA) # all others missing
    ) 
  ) %>% # then
  dplyr::filter( # Keep only respondents of immigrant origin,
    facntr == "No" & mocntr == "No") %>% # then
  group_by(cntry) %>% # Group data by country, then
  dplyr::summarize(
    # Weighted number of cases.
    wn = sum(pspwght, na.rm = TRUE), 
    # Weighted number of persons who see their group face racial discrimination.
    wn_rd = sum(racial_discr * pspwght, na.rm = TRUE), 
    # Weighted percent who see their group face racial discrimination.
    wperc_rd = (wn_rd / wn)  * 100) %>%
  arrange(desc(wperc_rd))
```
`r unhide()`

3. In which among all ESS countries do people on average show the highest *agreement* to the statement that gay women and men should be allowed to adopt children? `r fitb("France", width = "7")`
    + That is, give country-level summaries of the average agreement plus its 95% confidence interval. 
    + `wtd.mean()` from the `Hmsic` package estimates weighted means. 
    + Moreover, `wtd.var()` estimates weighted variances, and remember: $\text{SD} = \sqrt{\text{Var}}$.
    + Beware that we asked for the average agreement.
`r hide("R solution -> dont' peek to early ;) !")`
```{r}
ESS %>% # Use the ESS, then
  transmute( # Create new variables and only keep these new ones
    # Make the following variables factors:
    cntry = as_factor(cntry) %>% fct_drop(), 
    # Make the following variables numeric:
    pspwght = pweight*dweight,
    hmsacld = max(zap_labels(hmsacld), na.rm = TRUE) - zap_labels(hmsacld), #<<
  ) %>%
  group_by(cntry) %>% # Group data by country, så
  dplyr::summarize(
    n = sum(pspwght, na.rm = TRUE),
    mean_hmsacld = wtd.mean(hmsacld, weights = pspwght, na.rm = TRUE),
    sd_hmsacld = wtd.var(hmsacld, weights = pspwght, na.rm = TRUE) %>% sqrt(),
    se_hmsacld = sd_hmsacld / sqrt(n),
    min95 = mean_hmsacld - se_hmsacld * qt(p = 0.975, df = n),
    max95 = mean_hmsacld + se_hmsacld * qt(p = 0.975, df = n)) %>%
  arrange(desc(mean_hmsacld))
```
`r unhide()`
