---
title: "1 Hello R: Vectors"
summary: "In this first lecture you will get a gentle introduction to the statistical programming language R and some of its basic functionality."
author: Merlin Schaeffer & Friedolin Merhout
date: 2022-10-19
publishdate: 2021-09-03
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE, servr.interval = 0.5, width = 115, digits = 2)
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, 
  warning = FALSE, cache = FALSE,
  comment = "#", strip.white = TRUE)

library(webexercises)
```

In this first lecture you will get a gentle introduction to the statistical programming language R and some of its basic functionality. The lecture covers different operators, the idea behind R's workhorse functions, and basic data structures in R. The lecture is a bit abstract, like this line of code:
```{r}
(I_am_an_object <- seq(from = 2, to = 8))
```
But stay with it, you'll get the hang of it soon enough. You will also learn about the workflow of using RStudio, including how to set up a project and how to use R Scripts to organize your research and make it reproducible.

Lecture slides: [**Int_R_oduction**](/1-Hello_R_Vectors/1-Hello_R_Vectors.html)

Exercise: [**Web Excercise 1**](/exercises/exercise1.html)