---
title: "2 Data Frames and Tibbles"
summary: "This lecture will introduce you to data frames and tibbles, and how to work with them as well as with atomic vectors."
author: Merlin Schaeffer & Friedolin Merhout
date: 2022-10-19
publishdate: 2021-09-03
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE, servr.interval = 0.5, width = 115, digits = 2)
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, 
  warning = FALSE, cache = FALSE,
  comment = "#", strip.white = TRUE)
```

This lecture will introduce you to data frames and tibbles, and how to work with them as well as with atomic vectors. We will also cover packages - the source of R's versatility - and get to know basic functionality from the collection of packages known as tidyverse. A set of packages containing, among others, data of Star Wars characters:
```{r}
library(tidyverse)
starwars
```

In this session you will also learn how to access specific variables or cases from a tibble, how to do complex data transformations and recodes, and finally, how to use an API to import data from the European Social Survey.

Lecture slides: [**Data Frames and Tibbles**](/2-Data-Frames/2-Data-Frames.html)

Today's exercise: [**Web Excercise 2**](/exercises/exercise2.html)
