---
title: "3 Data Frames and Tibbles"
summary: "This lecture will introduce you to data frames and tibbles, the best way to organize data in R."
author: Merlin Schaeffer
date: 2021-09-17
publishdate: 2021-09-12
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE, servr.interval = 0.5, width = 115, digits = 2)
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, 
  warning = FALSE, cache = FALSE,
  comment = "#", strip.white = TRUE)
```

This lecture introduces you to data frames and tibbles, the best way to organize data. The tidyverse package contains, among others, a starwars tibble that neatly organizes information about different characters:
```{r}
library(tidyverse)
starwars
```

In this session you will learn how to access specific variables or cases from a tibble, how to do complex data transformations and recodes, and finally, how to use an API to import data from the European Social Survey.

Lecture slides: [**Data Frames and Tibbles**](/3-Data-Frames/3-Data-Frames.html)

Today's exercise: [**Web Excercise 3**](/exercises/exercise3.html)
