---
title: "4 Visualization II"
summary: "This lecture will continue your introduction to the basics of the grammar of graphics and ggplot2."
author: Merlin Schaeffer & Friedolin Merhout
date: 2022-10-20
publishdate: 2022-10-20
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE, servr.interval = 0.5, width = 115, digits = 2)
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, 
  warning = FALSE, cache = FALSE, fig.retina = 3,
  comment = "#", strip.white = TRUE)

# Add packages to library
library(tidyverse) # Add the tidyverse package to my current library.
library(haven) # Handle labelled data.
library(essurvey) # Add ESS API package to library.
library(ggplot2) # Allows us to create nice figures.

# Read ESS round 10 data
ESS <- read_spss("./../../assets/ESS10.sav")

ESS <- transmute(ESS, # Recode several variables & keep only the recoded ones (i.e., transmute vs mutate). #<<
                 idno = zap_labels(idno),
                 # Make the following variables factors:
                 cntry = as_factor(cntry), 
                 gndr = as_factor(gndr),
                 facntr = as_factor(facntr),
                 mocntr = as_factor(mocntr),
                 # Make the following variables numeric:
                 imbgeco = max(imbgeco, na.rm = TRUE) - zap_labels(imbgeco), # Also turn scale around.
                 imueclt = max(imueclt, na.rm = TRUE) - zap_labels(imueclt), # Also turn scale around.
                 imwbcnt = max(imwbcnt, na.rm = TRUE) - zap_labels(imwbcnt), # Also turn scale around.
                 agea = zap_labels(agea),
                 pspwght = pweight*dweight,
                 eduyrs = case_when(
                   eduyrs > 21 ~ 21, # Recode to max 21 years of edu.
                   eduyrs < 9 ~ 9, # Recode to min 9 years of edu.
                   TRUE ~ zap_labels(eduyrs) # Make it numeric.
                 ),
)

ESS <- dplyr::filter(ESS,
                     # Only respondents whose parents were born in country of interview.
                     facntr == "Yes" & mocntr == "Yes" &
                       # Only Eastern European countries:
                       (cntry == "Slovakia" | cntry == "Hungary" | cntry == "Czechia" | cntry == "Slovenia")
)

# Casewise deletion of missing values
ESS <- drop_na(ESS)
```

This lecture refreshes and builds up on yesterday's introduction to the basics of "the grammar of graphics". Specifically, you will learn how to deal with overplotting due to discrete responses, represent grouping variables in intuitive ways, and export your resulting visualizations.

Lecture slides: [**Visualization II**](/4-Visualization-II/4-Visualization-II.html)

Exercise: [**Web Excercise 4**](/exercises/exercise4.html)

```{r fig.width = 8, fig.height = 3.5}
ggplot(data = ESS, 
       mapping = aes(y = imwbcnt, x = factor(eduyrs), weight = pspwght)) +
  geom_boxplot() +
  geom_smooth(mapping = aes(group = 1)) +
  facet_wrap( ~ cntry, nrow = 1) + 
  labs(y = "Immigrants make country \n worse place to live", 
       x = "Years of Education")
```

