---
title: "4 Visualization I"
summary: "This lecture will introduce you to the basics of the grammar of graphics and ggplot2."
author: Merlin Schaeffer
date: 2021-09-17
publishdate: 2021-09-12
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE, servr.interval = 0.5, width = 115, digits = 2)
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, 
  warning = FALSE, cache = FALSE, fig.retina = 3,
  comment = "#", strip.white = TRUE)

# Add packages to library
library(tidyverse) # Add the tidyverse package to my current library.
library(haven) # Handle labelled data.
library(essurvey) # Add ESS API package to library.
library(ggplot2) # Allows us to create nice figures.

# Import the ESS round 9 data via the API
ESS <- import_rounds(rounds = 9, ess_email = "merlin.schaeffer@uni-koeln.de", format = "spss")

ESS <- transmute(ESS, # Recode several variables & keep only the recoded ones (i.e., transmute vs mutate). #<<
                 idno = zap_labels(idno),
                 # Make the following variables factors:
                 cntry = as_factor(cntry), 
                 gndr = as_factor(gndr),
                 facntr = as_factor(facntr),
                 mocntr = as_factor(mocntr),
                 # Make the following variables numeric:
                 imbgeco = max(imbgeco, na.rm = TRUE) - zap_labels(imbgeco), # Also turn scale around.
                 imueclt = max(imueclt, na.rm = TRUE) - zap_labels(imueclt), # Also turn scale around.
                 imwbcnt = max(imwbcnt, na.rm = TRUE) - zap_labels(imwbcnt), # Also turn scale around.
                 agea = zap_labels(agea),
                 pspwght = zap_labels(pspwght),
                 eduyrs = case_when(
                   eduyrs > 21 ~ 21, # Recode to max 21 years of edu.
                   eduyrs < 9 ~ 9, # Recode to min 9 years of edu.
                   TRUE ~ zap_labels(eduyrs) # Make it numeric.
                 ),
)

ESS <- dplyr::filter(ESS,
                     # Only respondents whose parents were born in country of interview.
                     facntr == "Yes" & mocntr == "Yes" &
                       # Only respondents from direct neighbors of Denmark:
                       (cntry == "Denmark" | cntry == "Germany" | cntry == "Sweden" | cntry == "Norway")
)

# Casewise deletion of missing values
ESS <- drop_na(ESS)
```

This lecture introduces you to the basics of "the grammar of graphics", which underlies the R package ggplot2. You will gain a basic understanding of how to visualize your data for exploratory purposes. In particular, you will be able to read and write R code such as the one below, which produces the figure shown beneath the code.

Lecture slides: [**Visualization I**](/4-Visualization-I/4-Visualization-I.html)

Today's exercise: [**Web Excercise 4**](/exercises/exercise4.html)

```{r fig.width = 8, fig.height = 3.5}
ggplot(data = ESS, 
       mapping = aes(y = imwbcnt, x = factor(eduyrs), weight = pspwght)) +
  geom_boxplot() +
  geom_smooth(mapping = aes(group = 1)) +
  facet_wrap( ~ cntry, nrow = 1) + 
  labs(y = "Immigrants make country \n worse place to live", 
       x = "Years of Education")
```

## Homework
1. Finish web exercise 3 and 4.
2. Read Chapter [3 Data Visualization](http://r4ds.had.co.nz/data-visualisation.html).
3. Read Chapter [7 Exploratory Data Analysis](http://r4ds.had.co.nz/exploratory-data-analysis.html).

