---
title: "5 Piping and Grouped Operations"
summary: "This lecture introduces you the %>% operator as neat way to organize your code."
author: Merlin Schaeffer & Friedolin Merhout
date: 2022-10-20
publishdate: 2022-10-20
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE, servr.interval = 0.5, width = 115, digits = 2)
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, 
  warning = FALSE, cache = FALSE, fig.retina = 3,
  comment = "#", strip.white = TRUE)

# Add packages to library
library(tidyverse) # Add the tidyverse package to my current library.
library(haven) # Handle labelled data.
library(essurvey) # Add ESS API package to library.
library(ggplot2) # Allows us to create nice figures.

# Import the ESS round 9 data via the API
ESS <- read_spss("./../../assets/ESS10.sav") %>%
  transmute( # Create new variables and keep only those
    cntry = as_factor(cntry), # Country of interview
    gndr = as_factor(gndr),
    facntr = as_factor(facntr), # Father born in cntry
    mocntr = as_factor(mocntr), # Mother born in cntry
    dscrgrp = as_factor(dscrgrp), # Belonging to discriminated group #<<
    dscrrlg = as_factor(dscrrlg), # Discriminated because of religion #<<
    rel_discr = case_when( #<<
      dscrgrp == "Yes" & dscrrlg == "Marked" ~ "Yes", #<<
      dscrgrp == "No" | (dscrgrp == "Yes" & dscrrlg != "Marked") ~ "No", #<<
      TRUE ~ as.character(NA)) %>% as_factor(), # all others missing, then change to factor #<<
    rel_discr_num = case_when(rel_discr == "Yes" ~ 1, 
                              rel_discr == "No" ~ 0,
                              TRUE ~ as.numeric(NA)),
    pspwght = pweight*dweight, # Post-stratification weights.     
    agea = zap_labels(agea), # Age
    eduyrs = case_when( # Education
      eduyrs > 21 ~ 21, # Recode to max 21 years of edu.
      eduyrs < 9 ~ 9, # Recode to min 9 years of edu.
      TRUE ~ zap_labels(eduyrs)) # Make it numeric.
  ) %>% # finish transmute, then (pipe result into) #<<
  dplyr::filter( # Keep only respondents of immigrant origin,
    facntr == "No" & mocntr == "No")  
```

This lecture introduces you to piping as a neat way to organize your code and make it more legible. Moreover you will also learn how to quickly calculate and estimate statistics by sub-populations, so as to compare them. 

```{r}
(ESS_cntry <- ESS %>% # use ESS, then
   group_by(cntry) %>% # group by cntry, then
   summarize( # Start summarize function.
     # weighted number of cases,
     wn = sum(pspwght, na.rm = TRUE),
     # weighted cases reporting to belong to a discriminated religious minority,
     wn_rd = sum(rel_discr_num * pspwght, na.rm = TRUE), 
     wperc_rd = (wn_rd / wn) * 100 # weighted %,
   )) # End of summarize.
```

This code shows how you can use `%>%`, `group_by()` and `summarize()` to quickly estimate the share of persons of immigrant origin who feel that they belong to a discriminated religious minority in the country in which they live.

Lecture slides: [**Piping and Grouped Operations**](/5-Piping/5-Piping.html)

Exercise: [**Web Excercise 5**](/exercises/exercise5.html)