---
title: "6 Visualization III"
summary: "This lecture will finalize our introduction to the basics of the grammar of graphics and ggplot2."
author: Merlin Schaeffer & Friedolin Merhout
date: 2022-10-20
publishdate: 2022-10-20
---

```{r setup, include = FALSE}
library(RefManageR)
options(htmltools.dir.version = FALSE, servr.interval = 0.5, width = 115, digits = 2)
knitr::opts_chunk$set(
  collapse = TRUE, message = FALSE, fig.retina = 3, error = TRUE,
  warning = FALSE, cache = FALSE, fig.align='center',
  comment = "#", strip.white = TRUE)

BibOptions(check.entries = FALSE, 
           bib.style = "authoryear", 
           style = "markdown",
           hyperlink = FALSE,
           no.print.fields = c("doi", "url", "ISSN", "urldate", "language", "note", "isbn", "volume"))
myBib <- ReadBib("./../../intRo.bib", check = FALSE)

# Add packages to library
library(tidyverse) # Add the tidyverse package to my current library.
library(haven) # Handle labelled data.
library(ggplot2) # Allows us to create nice figures.

# Import the ESS round 10
ESS <- read_spss("./../../assets/ESS10.sav") %>%
  transmute( # Create new variables and keep only those
    cntry = as_factor(cntry) %>% fct_drop(), # Country of interview
    gndr = as_factor(gndr),
    facntr = as_factor(facntr), # Father born in cntry
    mocntr = as_factor(mocntr), # Mother born in cntry
    dscrgrp = as_factor(dscrgrp), # Belonging to discriminated group #<<
    dscrrlg = as_factor(dscrrlg), # Discriminated because of religion #<<
    rel_discr = case_when( #<<
      dscrgrp == "Yes" & dscrrlg == "Marked" ~ "Yes", #<<
      dscrgrp == "No" | (dscrgrp == "Yes" & dscrrlg != "Marked") ~ "No", #<<
      TRUE ~ as.character(NA)) %>% as_factor(), # all others missing, then change to factor #<<
    rel_discr_num = case_when(rel_discr == "Yes" ~ 1, 
                              rel_discr == "No" ~ 0,
                              TRUE ~ as.numeric(NA)),
    pspwght = pweight*dweight, # Post-stratification weights.     
    agea = zap_labels(agea), # Age
    eduyrs = case_when( # Education
      eduyrs > 21 ~ 21, # Recode to max 21 years of edu.
      eduyrs < 9 ~ 9, # Recode to min 9 years of edu.
      TRUE ~ zap_labels(eduyrs)) # Make it numeric.
  ) %>% # finish transmute, then (pipe result into) #<<
  dplyr::filter((cntry == "Bulgaria" | cntry == "Croatia" | cntry == "France"))

ESS_cntry <- ESS %>% # use ESS, then
   group_by(cntry) %>% # group by cntry, then
   summarize( # Start summarize function. #<<
     wn = sum(pspwght, na.rm = TRUE), # weighted number of cases,
     wn_rd = sum(rel_discr_num * pspwght, na.rm = TRUE), # weighted number of cases who ...,
     wperc_rd = (wn_rd / wn) * 100, # weighted % who ...,
     wse_rd = sqrt(wperc_rd * (100 - wperc_rd) / wn), # Standard error of the percent,
     wmin95_rd = wperc_rd - wse_rd * qt(p = 0.975, df = wn), # Lower bound of 95% CI,
     wmax95_rd = wperc_rd + wse_rd * qt(p = 0.975, df = wn) # Upper bound of 95% CI,
   ) # End of summarize.

(ESS_cntry <- ESS_cntry %>% 
  mutate(discr_level = case_when(
      cntry == "France" ~ "Pronounced",
      TRUE ~ "Less pronounced") %>% fct_relevel("Pronounced")))
```

This lecture gives you the tools to visualize the summary statistics that you learned to generate in the last session. Moreover, we will discuss the remaining aspects of the grammar of graphics that we have not covered yet. At the end of this session, you will be able to generate near-publishable figures like the one below.

```{r fig.width = 7, fig.height = 3.5, echo = FALSE}
ggplot(data = ESS_cntry, mapping = aes(y = wperc_rd, x = reorder(cntry, wperc_rd))) +
  geom_segment(mapping = aes(color = discr_level, y = wmin95_rd, yend = wmax95_rd, xend = cntry), size = 6.5, alpha = 0.3) +
  geom_point(mapping = aes(fill = discr_level), size = 5, shape = 21, color = "white") +
  coord_flip() +
  labs(x = "Country", y = "% Who State That They Belong\n to a Discriminated Religious Minority in Their Country of Residence\n(Along with 95% Confidence Intervals)",
       color = "Level of Discrimination", fill = "Level of Discrimination",
       title = "Perceived Religious Discrimination", subtitle = "A Comparison of Three Countries",
       caption = "(Based on the European Social Survey 2020)") + 
  theme_minimal() +
  theme(legend.position = c(0.87, 0.27), legend.background = element_rect(fill = NA, color = NA))
```

Lecture slides: [**Visualization III**](/6-Visualization-III/6-Visualization-III.html)

Exercise: [**Web Excercise 6**](/exercises/exercise6.html)


## Homework
1. Finish web exercise 4 through 6.
